The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-08-05 script/en/script-en.tex
new float cryptoprocedure for crypto algorithms and procedures (chapter 5); fixed links to un-numbered chapters with phantomsection

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}
\usepackage{float}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,hypertexnames=false]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels and hypertexnames=false and place hyperref after float.
%Option debug helps finding problems.

\floatstyle{ruled}
\newfloat{sagecode}{!h}{loc}[chapter]
\floatname{sagecode}{Sage sample}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
%\newcommand{\href}[2]{#2}
\newcommand{\hypertag}[2]{#1}
%\newcommand{\hyperlink}[2]{#2}
%\newcommand{\hypertarget}[2]{#2}
\newtheorem{theorem}{Theorem}[section]
\newenvironment{Proof}[1]
  {\textbf{Proof #1} \\}
  {\hfill$\Box$ \\}
\newenvironment{example}[1]{\noindent\textbf{Example#1}}{}
\newenvironment{remark}[1]{\noindent\textbf{Comment#1}}{}

@@

\input{chapters/gnu-fdl-1.3.tex}
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begingroup
% remove extra vertical space from \listoffigure and \listoftables so that 
% it look similar to \listof{sagecode}
\setlength{\parskip}{0pt}
\clearpage
\listoffigures
\addcontentsline{toc}{chapter}{\listfigurename}

\clearpage
\listoftables
\addcontentsline{toc}{chapter}{\listtablename}

\clearpage
\listof{sagecode}{List of Sage Code Examples}
\addcontentsline{toc}{chapter}{List of Sage Code Examples}
\endgroup

\printindex

>>>>

\usepackage[flushmargin]{footmisc}
\usepackage{fullpage}
\usepackage{url}
% Literaturverzeichnis kapitelweise
\usepackage[labelstoglobalaux]{bibunits} % ohne labelstoglobalaux scheint man thebibilograpy und bibtex nicht mischen zu können
%\bibliographyunit[\section] % bibunits für das ganze Dokument aktivieren
\defaultbibliography{references}
\defaultbibliographystyle{abbrv}
\usepackage{float}
\usepackage[colorlinks=true,linkcolor=black,citecolor=black,urlcolor=black,bookmarksnumbered=true,pdfpagelabels,hypertexnames=false,debug]{hyperref}
%To reduce the number of hyperlink related 'pdfTeX warning's we use options 
%pdfpagelabels and hypertexnames=false and place hyperref after float.
%Option debug helps finding problems.

\floatstyle{ruled}
\newfloat{sagecode}{!h}{loc}[chapter]
\floatname{sagecode}{Sage sample}
\newfloat{cryptoprocedure}{!h}{lop}[chapter]
\floatname{cryptoprocedure}{Crypto Procedure}

@@

% \setlength{\textwidth}{460 pt}
% \hoffset-0.7in
\newtheorem{definition}{Definition}[section]
%\newcommand{\href}[2]{#2}
\newcommand{\hypertag}[2]{#1}
%\newcommand{\hyperlink}[2]{#2}
%\newcommand{\hypertarget}[2]{#2}
\newtheorem{theorem}{Theorem}[section]
\newenvironment{Proof}[1]{\noindent\textbf{Proof #1} \\}{\hfill$\Box$\par}
\newenvironment{example}[1]{\noindent\textbf{Example#1}}{}
\newenvironment{remark}[1]{\noindent\textbf{Comment#1}}{}

@@

\input{chapters/gnu-fdl-1.3.tex}
% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begingroup
% remove extra vertical space from \listoffigure and \listoftables so that 
% it look similar to \listof{sagecode}
%\setlength{\parskip}{0pt}
\renewcommand*{\addvspace}[1]{}

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{\listtablename}
\listoftables

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{List of Sage Code Examples}
\listof{sagecode}{List of Sage Code Examples}

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{List of Crypto Procedures}
\listof{cryptoprocedure}{List of Crypto Procedures}
\endgroup

\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Index}
\printindex
